Testing atlantisom: example bottom trawl survey index

### 2019-04-30 StandardSurveyTest.Rmd
standard survey NEUS example

initCCA <- FALSE
initNEUS <- FALSE
initNOBA <- TRUE

@@

@@

# general specifications for bottom trawl survey:
#   once per year at mid year
#   could generalize from the run.prm file: tstop/365 is n years of run
#   max result$biomass_ages$time/ n years of run is steps per year
#   take midpoint of 0, steps per year to start seq and go to max time by steps per year
#   hardcoded for NEUS 1.0 in trunk here
annualmidyear <- seq(3,251,5)

#other options for NEUS
annualspring <- seq(2,251,5)
annualfall <- seq(4,251,5)

#   all fish (and sharks!! need dogfish in NEUS)
survspp <- result$fgs$Name[result$fgs$IsTurnedOn==1 &
                           result$fgs$GroupType %in% c("FISH", "SHARK")]

@@

################# Below here is old from census, delete ################
# should return all model areas
boxpars <- load_box(d.name, box.file)
boxall <- c(0:(boxpars$nbox - 1))

# these are model specific, generalized above
# if(initCCA) boxall <- c(0:88) 
# if(initNEUS) boxall <- c(0:29)
# if(initNOBA) boxall <- c(0:59)

# should return all model output timesteps; need to generalize
if(initCCA) timeall <- c(0:100) 
if(initNEUS) timeall <- c(0:251)
if(initNOBA) timeall <- c(0:560)

# define set of species we expect surveys to sample (e.g. fish only? vertebrates?)
# for ecosystem indicator work test all species, e.g.
survspp <- funct.group.names

# to keep plots simpler, currently hardcoded for vertebrate/fished invert groups
if(initCCA) survspp <- funct.group.names[c(1:44, 59:61, 65:68)] 
if(initNEUS) survspp <- funct.group.names[1:21]
if(initNOBA) survspp <- funct.group.names[1:36]

@@

# read Atlantis output files
if(initCCA) {
  atBtxt2 <- read.table(here("atlantisoutput","CalCurrentSummitScenario1","outputCCV3BiomIndx.txt"), header=T)
  groupslookup <- load_fgs(dir = d.name, functional.groups.file)
  surveyB_frombio <- CCAsurveyB_frombio
}

if(initNEUS) {
  atBtxt2 <- read.table(here("atlantisoutput","NEUStest20160303","neusDynEffort_Test1_BiomIndx.txt"), header=T)
  groupslookup <- load_fgs(dir = d.name, functional.groups.file)
  surveyB_frombio <- NEUSsurveyB_frombio
}

if(initNOBA) {
  atBtxt2 <- read.table(here("atlantisoutput","NOBACERESGlobalSustainability","outputnordic_runresults_01BiomIndx.txt"), header=T) 
  groupslookup <- load_fgs(dir = d.name, functional.groups.file)
  surveyB_frombio <- NOBAsurveyB_frombio
}

@@

atBtxt2tidy <- atBtxt2 %>%
  select(Time:DIN) %>%
  #select(Time, FPL:DIN) %>%
  rename_(.dots=with(groupslookup, setNames(as.list(as.character(Code)), Name))) %>%
  gather(species, biomass, -Time) %>%
  filter(species %in% levels(surveyB_frombio$species))

#all species comparison, time intervals hardcoded for NEUS and NOBA
compareB <-ggplot() +
  geom_line(data=surveyB_frombio, aes(x=time/5,y=atoutput, color="survey census B"), 
            alpha = 10/10) +
  geom_point(data=atBtxt2tidy, aes(x=Time/365,y=biomass, color="txt output true B"),
             alpha = 1/10) + 
  #geom_line(data=surveyB_frombio_eff, aes(x=time/5,y=atoutput, color="stdeffB")) +
  #geom_line(data=surveyB_frombio_effsel, aes(x=time/5,y=atoutput, color="stdeffselB")) +
  geom_point(data=surveyB_frombio_effselcv, aes(x=time/5,y=atoutput, color="stdeffcvselB"),
              alpha = 1/2) +

@@

```{r matchBp4, fig.cap="Testing whether the survey census gives the same results as the Atlantis output biomass index file; last 9 species. Depending on the model, we may not show all species in this example."}
compareB + 
  facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 4, scales="free")

>>>>

initCCA <- FALSE
initNEUS <- TRUE
initNOBA <- FALSE

@@

We also read in previously generated survey census files based on true biomass results for comparison (see [TrueBioTest](https://sgaichas.github.io/poseidon-dev/TrueBioTest.html).)

```{r readsurvey1}

if(initCCA) {
  CCAsurveyB_frombio <- readRDS(file.path(d.name, paste0(scenario.name, "surveyBcensus.rds")))
}

if(initNEUS) {
  NEUSsurveyB_frombio <- readRDS(file.path(d.name, paste0(scenario.name, "surveyBcensus.rds")))
}

if(initNOBA) {
  NOBAsurveyB_frombio <- readRDS(file.path(d.name, paste0(scenario.name, "surveyBcensus.rds")))
}

@@

# general specifications for bottom trawl survey:
#   once per year at mid year
#   could generalize from the run.prm file: 
runpar <- load_runprm(d.name, run.prm.file)
noutsteps <- runpar$tstop/runpar$outputstep
stepperyr <- if(runpar$outputstepunit=="days") 365/runpar$toutinc
#   take midpoint of 0, steps per year to start seq and go to max time by steps per year
midptyr <- round(median(seq(1,stepperyr)))

annualmidyear <- seq(midptyr, noutsteps, stepperyr)

#   hardcoded for NEUS 1.0 in trunk here
# annualmidyear <- seq(3,251,5)
# #other options for NEUS
# annualspring <- seq(2,251,5)
# annualfall <- seq(4,251,5)

#   all fish (and sharks!! need dogfish in NEUS)
# could add groups "CEP" for cephalopod, "PWN" for prawn, etc
survspp <- funct.groups$Name[funct.groups$IsTurnedOn==1 &
                           funct.groups$GroupType %in% c("FISH", "SHARK")]

@@

# ################# Below here is old from census for reference, delete ################
# # should return all model areas
# boxpars <- load_box(d.name, box.file)
# boxall <- c(0:(boxpars$nbox - 1))
# 
# # these are model specific, generalized above
# # if(initCCA) boxall <- c(0:88) 
# # if(initNEUS) boxall <- c(0:29)
# # if(initNOBA) boxall <- c(0:59) 
# 
# # should return all model output timesteps; need to generalize
# if(initCCA) timeall <- c(0:100) 
# if(initNEUS) timeall <- c(0:251)
# if(initNOBA) timeall <- c(0:560) 
#   
# # define set of species we expect surveys to sample (e.g. fish only? vertebrates?)
# # for ecosystem indicator work test all species, e.g.
# survspp <- funct.group.names 
# 
# # to keep plots simpler, currently hardcoded for vertebrate/fished invert groups
# if(initCCA) survspp <- funct.group.names[c(1:44, 59:61, 65:68)] 
# if(initNEUS) survspp <- funct.group.names[1:21]
# if(initNOBA) survspp <- funct.group.names[1:36]

@@

# read Atlantis output files
if(initCCA) {
  atBtxt2 <- read.table(here("atlantisoutput","CalCurrentSummitScenario1","outputCCV3BiomIndx.txt"), header=T)
  groupslookup <- load_fgs(dir = d.name, functional.groups.file)
  stdsurveyB_frombio <- CCAstdsurveyB_frombio
  censusB_frombio <- CCAsurveyB_frombio
}

if(initNEUS) {
  atBtxt2 <- read.table(here("atlantisoutput","NEUStest20160303","neusDynEffort_Test1_BiomIndx.txt"), header=T)
  groupslookup <- load_fgs(dir = d.name, functional.groups.file)
  stdsurveyB_frombio <- NEUSstdsurveyB_frombio
  censusB_frombio <- NEUSsurveyB_frombio
}

if(initNOBA) {
  atBtxt2 <- read.table(here("atlantisoutput","NOBACERESGlobalSustainability","outputnordic_runresults_01BiomIndx.txt"), header=T) 
  groupslookup <- load_fgs(dir = d.name, functional.groups.file)
  stdsurveyB_frombio <- NOBAstdsurveyB_frombio
  censusB_frombio <- NOBAsurveyB_frombio
}

@@

atBtxt2tidy <- atBtxt2 %>%
  select(Time:DIN) %>%
  #select(Time, FPL:DIN) %>%
  rename_(.dots=with(groupslookup, setNames(as.list(as.character(Code)), Name))) %>%
  gather(species, biomass, -Time) %>%
  filter(species %in% levels(stdsurveyB_frombio$species))

censusB_frombio <- censusB_frombio %>%
  filter(species %in% levels(stdsurveyB_frombio$species))

#all species comparison, time intervals hardcoded for NEUS and NOBA
compareB <-ggplot() +
  geom_line(data=censusB_frombio, aes(x=time/5,y=atoutput, color="survey census B"), 
            alpha = 5/10) +
  geom_point(data=atBtxt2tidy, aes(x=Time/365,y=biomass, color="txt output true B"),
             alpha = 5/10) + 
  #geom_line(data=surveyB_frombio_eff, aes(x=time/5,y=atoutput, color="stdeffB")) +
  #geom_line(data=surveyB_frombio_effsel, aes(x=time/5,y=atoutput, color="stdeffselB")) +
  geom_point(data=stdsurveyB_frombio, aes(x=time/5,y=atoutput, color="stdeffcvselB"),
              alpha = 1/2) +

@@

```{r matchBp4, fig.cap="Testing whether the survey census gives the same results as the Atlantis output biomass index file; last 9 species. Depending on the model, we may not show all species in this example."}
if(!initNEUS){
  compareB + 
    facet_wrap_paginate(~species, ncol=3, nrow = 3, page = 4, scales="free") 
}
```
